---
title: "Homework 5"
output: github_document
date: "2023-11-14"
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(ggplot2)
library(dplyr)
```

## Problem 1

Read csv homicide data:

```{r}
homicide = read_csv("data/p1/homicide-data.csv", show_col_types = FALSE)
```

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicides_by_city_state = 
  homicide |>
  mutate(city_state = paste(city, state, sep = ", ")) 
```

```{r}
homicides_summarize_within_cities = homicides_by_city_state |>
  group_by(city_state)  |>
  mutate(unsolved = disposition %in% c("Closed without arrest","Open/No arrest")) |>
  summarise(total_homicides = n(), unsolved_homicides = sum(unsolved)) 
```

```{r}
homicides_summarize_within_cities
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore = 
  homicides_summarize_within_cities |> 
  filter(city_state == "Baltimore, MD")
baltimore_test = 
  prop.test(x = baltimore$"unsolved_homicides",n = baltimore$"total_homicides")
baltimore_result = 
  broom::tidy(baltimore_test) |> 
  select(estimate, conf.low, conf.high)
```

```{r}
baltimore_result
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
cities_result = homicides_summarize_within_cities |>
  mutate(
    prop_tests = 
      map2(unsolved_homicides, total_homicides,~prop.test(x = .x, n = .y)), tests_tidy = map(prop_tests, broom::tidy)
    ) |>
  unnest(tests_tidy) |>
  select(city_state, estimate, conf.low, conf.high)

cities_result
```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides

```{r}
ggplot(cities_result, aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  coord_flip() 
```

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
files_list = list.files(path = "data/p2", full.names = TRUE)
files_dataframe = tibble(file_name = files_list) |>
  mutate(data = purrr::map(file_name, ~ read_csv(.x, show_col_types = FALSE))) |>    
  mutate(file = substr(file_name, nchar(file_name)-10+1, nchar(file_name))) |> 
  mutate(file = str_replace(file, "\\..*", "")) |>
  separate(file, c("arm", "id"), sep = "_") |>   
  select(id, arm, data) |> 
  unnest(data) |>               
  pivot_longer(cols = week_1:week_8, names_prefix = "week_", names_to = "week", values_to = "data")
```

```{r}
files_dataframe
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
ggplot(files_dataframe, aes(x = week , y = data, group = id, color = arm)) + 
  geom_point() + 
  labs(x = "Week", y = "Data") 
```
The experimental group generally exhibits higher values than the control group, and these values tend to increase over time in the experimental group.

## Problem 3

For each dataset, save μ and the p-value arising from a test of H:μ=0 using α=0.05
Repeat the above for μ={1,2,3,4,5,6}, and complete the following:

```{r}
each_sim = function(mu, n=30, sigma=5) {
  sample = rnorm(n, mu, sigma) 
  sample_t = t.test(sample) 
  sample_t |> 
    broom::tidy() |> 
    select(c("estimate", "p.value"))
}

results =
  expand_grid(true_mu = 0:6, nsims = 1:5000) |>
  mutate(temp = map(true_mu, each_sim)) |>
  unnest(temp) |>
  group_by(true_mu) |>
  mutate(rej_null = p.value < 0.05) |>
  summarise(power = mean(rej_null), avg = mean(estimate),avg_rej = mean(estimate[rej_null])) 
```

```{r}
results
```


Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

```{r}
results |>
  ggplot(aes(x = true_mu, y = power)) +
  geom_point() +
  labs(x = "True Value of µ", y = "Power")
```

The power increases as the true value of µ rises. When the true value of µ surpasses 4, the power remains at 1, when true value of µ is small, the power is also very low.


Make a plot showing the average estimate of μ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ  only in samples for which the null was rejected on the y axis and the true value of μ  on the x axis. Is the sample average of μ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

```{r}
results |>
  ggplot(aes(x = true_mu, y = avg)) +
  geom_point() +
  labs(x = "True Value of µ", y = "Average Estimate of µ")
```
The average estimate of µ is very close to the true value of µ.


```{r}
results |>
  ggplot(aes(x = true_mu, y = avg_rej)) +
  geom_point() +
  labs(x = "True Value of µ", y = "Average Estimate of µ Rejected")
```
When the true value of µ is 0,the sample average of μ across tests for which the null is rejected approximately not equal to the true value of μ, but when the true value of µ greater than 1, the sample average of μ across tests for which the null is rejected approximately equal to the true value of μ.
